Cluster Difference Imaging Photometric Survey. Vetting Report Description Document

### 2020-01-11 doc/vetting_report_documentation/doc_TeX/ms.tex
vetting report docs
doc: clarify "neighborhood" definition

\begin{abstract}
To find planet candidates in clusters,
we make vetting reports using our light-curves \citep{bouma_cdips_2019} and
auxiliary data.
This document describes the CDIPS planet candidate vetting reports
uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-12-15 through present.
Earlier version of this document are available at
  \url{lgbouma.com/cdips_documentation/}.
\\

@@

Figure~\ref{fig:pg7} shows the labeled quantities from the target
star, the neighborhood, and the ``cluster members'' reported by
\citet{cantat-gaudin_gaia_2018}, \cite{kounkel_untangling_2019}, or
\citet{Kharchenko_et_al_2013}.  The top three subplots intentionally
omit the labelled cluster members, in order to give the user their own
by-eye assessment of whether they see clusters in the neighborhood,
and whether the target star is within those clusters.
The middle three subplots overplot cluster members from the reference
noted in the legend.

>>>>

\begin{abstract}
To find planet candidates in clusters,
we make vetting reports using our light-curves \citep{bouma_cdips_2019} and
auxiliary data.
This document describes the CDIPS planet candidate vetting reports
uploaded by \texttt{lbouma} to ExoFOP-TESS 2019-12-15 through present.
Earlier versions of this document are available at
  \url{lgbouma.com}.
\\

@@

The cluster members (black points) and the neighborhood members (gray
points) are {\it mutually exclusive sets}. After the stars are
randomly selected from the volume described above, any overlapping
stars between the group and the neighborhood samples are removed from
the neighborhood sample.

Figure~\ref{fig:pg7} shows the labeled quantities from the target
star, the neighborhood, and the ``cluster members'' reported by
\citet{cantat-gaudin_gaia_2018}, \cite{kounkel_untangling_2019}, or
\citet{Kharchenko_et_al_2013}.  The top three subplots intentionally
omit the labelled cluster members, in order to give the user their own
by-eye assessment of whether they see clusters in the neighborhood (as
might happen if the membership labelling is {\it incomplete}),
and whether the target star is within those clusters.
The middle three subplots overplot cluster members from the reference
noted in the legend.
